---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r}
library(dplyr)
library(ggplot2)
unzip("activity.zip")
data <- read.csv("activity.csv")
data <- tbl_df(data)
data <- filter(data, !is.na(steps))
data <- group_by(data,date)
```


## What is mean total number of steps taken per day?

{r}
meow <- summarise(data1,mean(steps),median(steps))
names(meow) <- c("date","mean","median")
g1 <- ggplot(meow,aes(date,mean))
g1 + geom_bar(stat = "identity")

### the total number of steps taken each day is:
```{r}
data1 <- summarise(data,sum(steps))
data1
```
```{r echo=TRUE}
plot(data1)
```

### The mean and median of the daily steps are:
```{r}
meow <- summarise(data,mean(steps),median(steps))
names(meow) <- c("date","mean","median")
g1 <- ggplot(meow,aes(date,mean))
g1 + geom_bar(stat = "identity")
g <- ggplot(meow,aes(date,median))
g + geom_bar(stat = "identity")
```

*the mean of all days is:`r mean(meow$mean)`

*The median is: `r median(meow$median)`

## What is the average daily activity pattern?

```{r}
data <- read.csv("activity.csv")
dat <- filter(data,!is.na(steps))
arr <- levels(data$date)

q <- length(arr)
q
count <- 0
for(i in 2:q){
  if(count == 0){
    woof <- select(filter(dat, date == arr[i]),steps)
    count <- 1
    count
    woof
  }
  else{
    if(dim(select(filter(dat,date == arr[i]),steps))[1] != 0){
      woof <- cbind(woof,select(filter(dat,date == arr[i]),steps))
    }
  }
}
woof <- cbind(woof,select(filter(dat,date == arr[2]),interval))

woof <- tbl_df(woof)
names(woof)<- c(1:53)
names(woof)[54] <- "interval"
woof1 <- mutate(woof,average = rowSums(woof)/ncol(woof))

p <- max(woof1$average)
best_time <- select(filter(woof1,average == p), interval)
```

* the max average is `r p ` found at the time interval `r best_time`

```{r}
with(woof1,plot(interval,average,type = "l"))
```




## Imputing missing values

```{r}
data_nas <- filter(data,is.na(steps) == TRUE)
```
###Then number of NA terms is: `r dim(data_nas)[1]`
### we would use the daily means calculated earlier to fill in these numbers in order to have fuller data





## Are there differences in activity patterns between weekdays and weekends?
